---
title: "Map-WP4"
author: "Emilia Marie Rolander Langkjær"
date: '2022-05-30'
output: html_document
---

#This R markdown is creating a map over Iceland containing relevant geological information as well as sites relevant to the project.

Marine map as done in https://mikkovihtakari.github.io/ggOceanMaps/articles/ggOceanMaps.html 

Load in the packages for ocean mapping
```{r}
library(ggOceanMapsData)
library(ggOceanMaps)
library("rgdal")
```

We map using the basemap command
```{r}
basemap(limits = 60)
```

Now we will specify the area we want to map. 
```{r}
basemap(limits = c(-25, -12, 63, 67))

```

Now we add on the depth of the ocean.
```{r}
basemap(limits = c(-25, -12, 63, 67), bathymetry = TRUE)
```

We can also add glaciers
```{r}
basemap(limits = c(-25, -12, 63, 67), bathymetry = TRUE, glaciers = TRUE)
```
Let's zoom into the north icelandic shelf
```{r}
basemap(limits = c(-21.5, -16.5, 65.5, 67), bathymetry = TRUE)
```


Let's put in some data points.
```{r}
site_core <- data.frame(lon = c(-17.700265, -18.169859, -18.527697, -19.50553), lat = c(66.551726, 66.236195, 66.213897, 66.500766))

basemap(limits = c(-21.5, -16.5, 65.5, 67), bathymetry = TRUE)+
  geom_point(data = transform_coord(site_core), aes(x = lon, y = lat), color = "red")
```

Right now we can't add the data points on land - I'll have to figure out how ot do that. 

Let's work on the layout of this figure now. 

```{r}
basemap(limits = c(-21.5, -16.5, 65.5, 67), bathymetry = TRUE, land.col = "dimgray", land.border.col = NA)+
  geom_point(data = transform_coord(site_core), aes(x = lon, y = lat), color = "red")
```

Adding scalebar and north arrow
```{r}
basemap(limits = c(-21.5, -16.5, 65.5, 67), bathymetry = TRUE, land.col = "darkgrey", land.border.col = NA)+
  geom_point(data = transform_coord(site_core), aes(x = lon, y = lat), color = "red")+
  annotation_scale(location = "br") + 
  annotation_north_arrow(location = "tr", which_north = "true")
```
Let's resize the north arrow
```{r}
basemap(limits = c(-21.5, -16.5, 65.5, 67), bathymetry = TRUE, land.col = "darkgrey", land.border.col = NA)+
  geom_point(data = transform_coord(site_core), aes(x = lon, y = lat), color = "red")+
  annotation_scale(location = "br") + 
  annotation_north_arrow(location = "tr", which_north = "true", height = unit(0.9, "cm"), width = unit(0.9, "cm"))
```

Let's try without the zoom
```{r}
basemap(limits = c(-25, -12, 63, 67), bathymetry = TRUE, glaciers = TRUE, land.col = "darkgrey", land.border.col = NA) + 
  geom_point(data = transform_coord(site_core), aes(x = lon, y = lat), color = "red")+
  annotation_scale(location = "br") + 
  annotation_north_arrow(location = "tr", which_north = "true", height = unit(0.9, "cm"), width = unit(0.9, "cm"))
```

